### 2024-05-07 thesis/chapters/appendix/E-work-plan.tex
Contents of digital medium

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in k-NN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning k-NN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for k-NN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump. Desihn the firmware for new datalogger.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions and visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

In reality, these tasks switched order because between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study. Only then from \nth{4} to \nth{11} week the main focus was on experiments with the MaFaulDa.

Lastly, preliminary measurements were conducted, as was the plan. Requirements were presented for the new sensor device and its firmware.
\clearpage
\newpage

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week  & Build and debug hardware of vibration logger with the consultant. 
\\ \hline
\nth{2} week & Implement and test firmware on standing fan for logging signal to SD card.
\\ \hline
\nth{3} week & First compressor (\nth{20} February) and water pump (\nth{27} and \nth{28} February) vibration measurements and their fault and frequency analysis. 
 \\ \hline
\nth{4} week & Replace two time domain features and evaluate on MaFaulDa and own dataset. Repeated measurement of compressors (\nth{5} March).
 \\ \hline
\nth{5} week & Perform PCA analysis of whole feature sets. Consultation about methods for own dataset evaluation.
 \\ \hline
\nth{6} week  & Consultation with experts in SjF STU. Formulate research goals for scientific paper and create graphs of the model results. Experiment with k-value and number of features to reach better accuracy. Repeated measurement of compressors (\nth{19} March).
 \\ \hline
\nth{7} week & Repeated measurement of water pumps (\nth{26} and \nth{27} March). Request and download data about pumps from KSB Cloud.
 \\ \hline
 \nth{8} week & Write up complete paper and submit to IIT.SRC student conference after feedback from supervisor.
 \\ \hline
 \nth{9} week & Refactor jupyter notebooks nad apply different labeling strategy applied in paper to incremental learning.
 \\ \hline
  \nth{10} week & Write up implementation chapter of the thesis.
 \\ \hline
  \nth{11} week & 
 \\ \hline
  \nth{12} - \nth{15} week &  
 \\ \hline
\end{tabular}
\end{table}

The aim of final semestre was to gather own dataset from compressors and water pumps with custom data logger. The k-NN model was validated with diffrent hyperparameters.

>>>>

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about the plan for a machine to measure in the data center and a better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in k-NN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning k-NN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for k-NN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump. Design the firmware for the new datalogger.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions and visualization export. Finish writing a chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

In reality, these tasks switched order because, between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study. Only then since \nth{4} until \nth{11} week, the main focus was on experiments with the MaFaulDa.

Lastly, preliminary measurements were conducted, as was the plan. The requirements were presented for the new sensor device and its firmware.
\clearpage
\newpage

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week  & Build and debug hardware of data logger with the consultant. 
\\ \hline
\nth{2} week & Implement and test firmware on standing fan for logging signal to SD card.
\\ \hline
\nth{3} week & First compressor (\nth{20} February) and water pump (\nth{27} and \nth{28} February) vibration measurements and their fault and frequency analysis. 
 \\ \hline
\nth{4} week & Replace two time-domain features and evaluate on MaFaulDa and own dataset. Repeated measurement of compressors (\nth{5} March).
 \\ \hline
\nth{5} week & Perform PCA analysis of whole feature sets. Consultation about methods for own dataset evaluation.
 \\ \hline
\nth{6} week  & Consultation with experts in SjF STU. Formulate research goals for scientific paper and create graphs of the model results. Experiment with the k-value and number of features to reach better accuracy. Repeated measurement of compressors (\nth{19} March).
 \\ \hline
\nth{7} week & Repeated measurement of water pumps (\nth{26} and \nth{27} March). Request and download data about pumps from KSB Cloud.
 \\ \hline
 \nth{8} week & Write up complete paper and submit to IIT.SRC student conference after feedback from supervisor.
 \\ \hline
 \nth{9} week & Refactor Jupyter notebooks and apply different labeling strategies applied in paper to incremental learning.
 \\ \hline
  \nth{10} - \nth{13} week & Update design chapter and finish text according to figures generated by experiments.
 \\ \hline
\end{tabular}
\end{table}

The final semester aimed at gathering dataset from compressors and water pumps with the accelerometer data logger. The k-NN model was validated with different hyperparameters. The data collection finished sooner in \nth{7} week whereas originally it was planned until \nth{10} week because it became apparent that during a such short period, the change in machine vibrations would be negligible. The preparation for IIT.SRC conference was also not originally planned and took time away from finishing the thesis.

### 2024-05-07 thesis/chapters/appendix/F-digital-medium.tex
Refactor jupyter
Contents of digital medium

\thispagestyle{empty}
\setcounter{figure}{0}
\chapter{Contents of the digital medium}
\pagenumbering{arabic}
\renewcommand*{\thepage}{E-\arabic{page}}
\par Evidenčné číslo práce v informačnom systéme: \RegNo
\par Obsah digitálnej časti práce (archív ZIP):
\par Názov odovzdaného archívu:

>>>>

\thispagestyle{empty}
\setcounter{figure}{0}
\chapter{Digital medium}
\pagenumbering{arabic}
\renewcommand*{\thepage}{E-\arabic{page}}
\par Registration number of thesis in AiS: \RegNo
\par Contents of the digital medium:
\par Name of submitted archive directory: DP\_MiroslavHajek.zip
\par Notice: Digital medium has more than 1 GiB and is available to the thesis supervisor.
\par The MaFaulDa dataset is publically available at: \url{https://www02.smt.ufrj.br/~offshore/mfs/database/mafaulda/full.zip}

\begin{itemize}[noitemsep]
\item[\textbf{>}] \textbf{datasets} - raw vibration data from machinery, and reports that took long to calculate.
	\begin{itemize}[noitemsep]
	\item[\textbf{>}] \textbf{FluidPump.zip} - custom recorded dataset of vibrations from air compressors and water pumps
	\item[\textbf{>}] \emph{MAFAULDA.zip} - placeholder where the downloaded MaFaulDa dataset should be placed
	\item[\textbf{>}] \textbf{best-subset} - the subset of features chosen to three-member subsets most frequently
	\item[\textbf{>}] \textbf{features} - features extracted from datasets in multiple domains
	\item[\textbf{>}] \textbf{ksb-cloud} - data exported from KSB cloud monitoring of vibration rms velocity and frequency waveform for chosen dates.
	\item[\textbf{>}] \textbf{misc-fluid-pump} - other non-standard measurements from pumps such as during speed up, slow down, or noise.
	\item[\textbf{>}] \textbf{knn-accuracy-distribution} - 
	\item[\textbf{>}] \textbf{knn-incremental-accuracy} - The incremental k-NN model accuracy after each sample for various lengths of tumbling window and gaps between labels 
	\item[\textbf{>}] \textbf{standing-fan} - audio for an estimate of fan rotational speed and measurements done in firmware verification on the back, side, and front of the fan.
	\end{itemize}
\item[\textbf{>}] \textbf{docs} - the documentation generated from source code comments  using automated tool
	\begin{itemize}[noitemsep]
	\item[\textbf{>}] \textbf{html-notebooks} - export of Jupyter notebooks for all basic configurations in HTML format
	\item[\textbf{>}] \textbf{doxygen} - documentation of \emph{firmware} 
	\item[\textbf{>}] \textbf{sphinx} - documentation of \emph{vibrodiagnostics} package
	\end{itemize}
\item[\textbf{>}] \textbf{firmware} - source code in \emph{main} directory for accelerometer data logger firmware written in C language with ESP-IDF SDK. The script \emph{bin2tsv.py} converts files saved to SD card in binary format to a tsv file.
\item[\textbf{>}] \textbf{notebooks} - Jupyter notebooks for data exploration, data analysis, and machine learning on provided datasets
\item[\textbf{>}] \textbf{vibrodiagnostics} - Python package of commonly used function in Jupyter notebooks for data processing
\end{itemize}

### 2024-05-07 thesis/chapters/preliminaries/acknowledgments.tex
Contents of digital medium

\vspace*{\fill}
\section*{Poďakovanie}
{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorby omnoho viac než zachytávajú slová na stránkach. Srdečná vďaka patrí školiteľovi Ing.~Marcelovi Balážovi,~PhD. a konzultantovi Ing.~Lukášovi Doubravskému z firmy R-DAS,~s.r.o. Obaja boli otvorení mojim všemožným nápadom a neochvejne ma podporovali v ich realizácii aj cez mnohé ťažkosti. Za praktický expertný pohľad na vibrodiagnostiku vďačím prof. Ing.~Stanislavovi Žiaranovi,~CSc. a Ing.~Ondrejovi Chlebovi,~PhD. zo Strojníckej fakulty STU. Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petera Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov. Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných prvkov na merania v klimatizáciach pre dátové centrá a sprístupnenie kompresorov. Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy. Nuž a v konečnom dôsledku som mal niekedy len viac šťastia ako rozumu.}
\vspace{3cm}

>>>>

\vspace*{\fill}
\section*{Poďakovanie}
{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorby omnoho viac než zachytávajú slová na stránkach. Srdečná vďaka patrí školiteľovi Ing.~Marcelovi Balážovi,~PhD. a konzultantovi Ing.~Lukášovi Doubravskému z firmy R-DAS,~s.r.o. Obaja boli otvorení mojim všemožným nápadom a neochvejne ma podporovali v ich realizácii aj cez mnohé ťažkosti. Za praktický expertný pohľad na vibrodiagnostiku vďačím prof. Ing.~Stanislavovi Žiaranovi,~CSc. a Ing.~Ondrejovi Chlebovi,~PhD. zo Strojníckej fakulty STU. Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petra Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov. Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných prvkov na merania v klimatizáciach pre dátové centrá a sprístupnenie kompresorov. Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy. Nuž a v konečnom dôsledku som mal niekedy len viac šťastia ako rozumu.}
\vspace{3cm}
